The promise of community driven preprints in ecology and evolution

### 2024-04-30 ms/ms.qmd
updates

# Acknowledgements
We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE). We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted. Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Committee, who have helped to make *EcoEvoRxiv* a success. This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper. DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).

>>>>

# Acknowledgements
We would like to thank the California Digital Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE). We would also like to thank Gabriela Hidalgo and Daisy Larios for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted. Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Committee, who have helped to make *EcoEvoRxiv* a success. This paper emerged from a hackathon at the 2023 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper. DWAN would also like to thank the Australian Research Council for a Future Fellowship (FT220100276).
